On-the-fly Algorithms for GKAT Equivalences \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-01-17 main.tex
minor tweaks

\begin{corollary}\label{thm:norm-bisim-exists-unique}
    For any bisimulation between two normalized GKAT coalgebra \({∼} ⊆ \norm(S) × \norm(U)\), a greedy bisimulation \(≈\) with \(∼\) as underlying bisimulation exists and is unique.
\end{corollary}

@@

\begin{proof}
    The \(⟹\) direction, we let \(∼_d\) be defined as in~\Cref{thm:dead-construction-greedy-bisim}.
    Because \({≈} ⊑ {∼_d}\) and~\Cref{thm:norm-sub-coalg}, \(\norm(≈) ⊑ \norm(∼_d)\). 
    Because \(\norm(∼_d)\) is a bisimulation between \(\norm(S)\) and \(\norm(U)\), therefore \(\norm(≈)\) is a bisimulation by~\cref{thm:}

@@

We then establish the correctness of greedy bisimulation, i.e. it is equivalent to trace equivalence.

\begin{theorem}[Correctness]
    Given two states in GKAT coalgebras \(s ∈ S\) and \(u ∈ ,U\), there exists a greedy bisimulation \({≈} ⊆ S × U\) s.t. \(s ≈ u\), if and only if \(⟦s⟧_S = ⟦u⟧_U\).
\end{theorem}

\begin{proof}
    \(⟹\) direction, because normalization preserves carrier set, therefore \((s, u) ∈ \norm(≈)\).
    And because \(\norm(≈)\) is a bisimulation between \(\norm(S)\) and \(\norm(U)\) (\Cref{thm:greedy-bisim-iff-norm-bisim}), \(⟦s⟧_S = ⟦u⟧_U\).

    \(⟸\) direction, because \(⟦s⟧_S = ⟦u⟧_U\), then by~\cref{thm:norm-bisim-correctness}, then there a bisimulation \(∼ ⊆ \norm(S) × \norm(U)\) s.t. \(s ∼ u\). 
    Because~\Cref{thm:norm-bisim-exists-unique}, therefore there exists a greedy bisimulation \(≈\) with \(∼\) as its underlying bisimulation. 
    Because the carriers \({∼} ⊆ {≈}\), therefore \(s ∼ u\) implies \(s ≈ u\).
\end{proof}

Despite proving many desirable structural properties, the definition of greedy bisimulation is still coalgebraic.
To design an equivalence-checking algorithm to construct a greedy bisimulation still requires turning the coalgebra into a set of concrete criteria, that can be checked by an algorithm.
In the following theorem, we will present four conditions, and the algorithm will be largely based on recursively checking these conditions to establish a greedy bisimulation.

>>>>

\begin{corollary}\label{thm:greedy-bisim-exists-unique}
    For any bisimulation between two normalized GKAT coalgebra \({∼} ⊆ \norm(S) × \norm(U)\), a greedy bisimulation \(≈\) with \(∼\) as underlying bisimulation exists and is unique.
\end{corollary}

@@

\begin{proof}
    The \(⟹\) direction, we let \(∼_d\) be defined as in~\Cref{thm:dead-construction-greedy-bisim}.
    Because \({≈} ⊑ {∼_d}\) and~\Cref{thm:norm-sub-coalg}, \(\norm(≈) ⊑ \norm(∼_d)\). 
    Because \(\norm(∼_d)\) is a bisimulation between \(\norm(S)\) and \(\norm(U)\), therefore \(\norm(≈)\) is a bisimulation (\Cref{thm:greedy-bisim-iff-norm-bisim}).

@@

% Similar to the correctness of bisimulation between normalized coalgebra (\Cref{thm:norm-bisim-correctness}), we also establish a correctness theorem for greedy bisimulation, i.e. there exists

% \begin{theorem}[Correctness]
%     Given two states in GKAT coalgebras \(s ∈ S\) and \(u ∈ ,U\), there exists a greedy bisimulation \({≈} ⊆ S × U\) s.t. \(s ≈ u\), if and only if \(⟦s⟧_S = ⟦u⟧_U\).
% \end{theorem}

% \begin{proof}
%     \(⟹\) direction, because normalization preserves carrier set, therefore \((s, u) ∈ \norm(≈)\).
%     And because \(\norm(≈)\) is a bisimulation between \(\norm(S)\) and \(\norm(U)\) (\Cref{thm:greedy-bisim-iff-norm-bisim}), \(⟦s⟧_S = ⟦u⟧_U\).

%     \(⟸\) direction, because \(⟦s⟧_S = ⟦u⟧_U\), then by~\cref{thm:norm-bisim-correctness}, then there a bisimulation \(∼ ⊆ \norm(S) × \norm(U)\) s.t. \(s ∼ u\). 
%     Because~\Cref{thm:greedy-bisim-exists-unique}, therefore there exists a greedy bisimulation \(≈\) with \(∼\) as its underlying bisimulation. 
%     Because the carriers \({∼} ⊆ {≈}\), therefore \(s ∼ u\) implies \(s ≈ u\).
% \end{proof}

Despite proving many desirable structural properties, the definition of greedy bisimulation is still coalgebraic.
In order for our equivalence-checking algorithm to construct a greedy bisimulation, we need to turn the coalgebra into a set of concrete criteria, that can be checked by an algorithm.
In the following theorem, we will present such necessary and sufficient conditions to construct a greedy bisimulation.
Our algorithm will be largely based on recursively checking these conditions to establish a greedy bisimulation.
